RJObject Paper

### 2014-06-21 Documents/Paper/ms.tex
Writing about proposals

>>>>

Most of the proposals involve changing one (or a subset) of the parameters
and/or hyperparameters while keeping the others fixed.

\subsection{Proposals that modify $N$}
The first kind of proposal we consider are proposals that change the
dimension of the model, i.e. proposals that change the value of $N$. By
necessity, these will also change the parameters $\{x_i\}_{i=1}^N$ because
the number of parameters will be changed.
